\chapter*{Abstract}
\begin{flushleft}
    In the modern world the concept of a smart home and smart facilities are not a distant dream anymore.
    Ideally, using the smart features offered by the modern era we want to monitor our home or facilities
    in detail. Not only we want our home or facilities to be secure from the intruders and prevent the theft
    or damage of our belongings we also want to keep tabs on who is entering and leaving the home or facility
    at what times. This can be useful for identifying missing elements to solving serious crimes.
    \vspace{.5cm}

    Simple `Access control keypads' and `Key fobs' alone are not secure enough anymore. Since `Key fobs' and 
    passwords can easily be stolen. I propose a `Two Factor Authentication System' for access to the home or
    facility using a combination of both `Previous knowledge' (such as passwords) or `Belongings' (such as key fob)
    and a `Biometric Vector' (such as Facial Data). This will ensure the person having the right key is also the right 
    person with the adequate clearance or permission to enter the home or facility. There is one more thing to note, 
    often `The chain is as strong as it\'s weakest link', so we have to think about other entry point than the main
    door. We can add sensors to windows and other potential entry point for intrusion detection. 
    \vspace{.5cm}

    We have achieved this project goals with a combination of single board computers and micro controllers as 
    the main processing side of the project. Networking elements and data collection points (i.e. cameras and sensors) 
    were also integral part of this project. 
    \vspace{.5cm}

    \textbf{Key words: }Raspberry Pi, Home Automation, Smart Home, Intrusion Detection, Home Security, Face Recognition,
    Visitor Monitoring, Entry Logging


\end{flushleft}
